---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggbody

<!-- badges: start -->
<!-- badges: end -->

ggbody uses corporal atlases (curated in fantastic packages like ggseg and gganatogram) and experiments with APIs like ggfips (us counties) and ggnc (north carolina).  That is, the aesthetic 'where' is the name of the region and flat files without region perimeter information can be used as the data frame input. 

## Installation

You can install the development version of ggbody from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("EvaMaeRey/ggbody")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(tidyverse)
library(ggbody)
## basic example code

library(ggplot2)
c("fusiform",
"inferior parietal"	,
"insula", "precentral"
) %>% tibble(my_region = .) %>%
 mutate(value = 1:4) %>%
 mutate(name = letters[1:4] %>% as.factor()) %>%
 ggplot() +
 aes(region = my_region, fill = value) +
 geom_sf(data = ggseg::dk$data,
         aes(region = NULL, fill = NULL) # huh?  required?
 ) +
 geom_sf_brainsegs(alpha = .5)
```


```{r}
ggplot() + 
  stamp_sf_brainsegs(fill = "blue")


ggplot() +
  stamp_sf_brainsegs(alpha = .5, fill = "blue") +
  stamp_sf_brainsegs(hemi = "left", fill = "black") +
  stamp_sf_brainsegs(side = "lateral", hemi = "right", fill = "green") +
  stamp_sf_brainsegs(region = "insula", fill = "pink")

```
