---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggbody

<!-- badges: start -->
<!-- badges: end -->

ggbody uses corporal atlases (curated in fantastic packages like ggseg and gganatogram) and experiments with APIs like those in ggfips (us counties) and ggnc (north carolina).  That is, position aesthetic is allowed which will join up the atlas polygons in the background via the ggplot compute mechanisms.  This allows flat files without region perimeter information to be used as the data frame input.  In addition, there are stamp functions which allow geometries to be accessed without referring to any dataframe at all, but by the name of the region (or meta or sub region). 

## Installation

You can install the development version of ggbody from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("EvaMaeRey/ggbody")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(tidyverse)
library(ggbody)
## basic example code

library(ggplot2)

set.seed(12345)
dk_flat %>% 
  slice_sample(n = 5)

set.seed(12345)
dk_flat %>% 
  slice_sample(n = 5) %>% 
  mutate(id = row_number()) %>% 
 ggplot() +
 aes(region = region, fill = id) +
 stamp_dk_brain(aes(region = NULL, fill = NULL)) + # nulling out work around needs to be addressed
 geom_dk_brain(alpha = .5)
```


```{r}
ggplot() + 
  stamp_dk_brain(fill = "blue")

ggplot() +
  stamp_dk_brain(alpha = .5, fill = "blue") +
  stamp_dk_brain(hemi = "left", fill = "grey") +
  stamp_dk_brain(side = "lateral", hemi = "right", fill = "green") +
  stamp_dk_brain(region = "insula", fill = "darkred")


ggplot() +
  stamp_dk_brain(alpha = .5, fill = "blue") +
  stamp_dk_insula(fill = "darkred") + 
  stamp_dk_rostral_middle_frontal(fill = "goldenrod2")


ggplot() +
  stamp_dk_brain() +
  stamp_dk_side_lateral(fill = "cornflowerblue") +
  stamp_dk_insula(fill = "darkred") + 
  stamp_dk_rostral_middle_frontal(fill = "goldenrod2")
```
# issues

fill aesthetic cannot be character/factor/TF

```{r, error=T}
dk_flat %>% 
  slice_sample(n = 5) %>% 
  mutate(id = LETTERS[1:5]) %>% 
 ggplot() +
 aes(region = region, fill = id) +
 stamp_dk_brain(aes(fill = NULL, region = NULL)) +
 geom_dk_brain(alpha = .5)


dk_flat %>% 
  slice_sample(n = 5) %>% 
  mutate(id = LETTERS[1:5] %>% as.factor()) %>% 
 ggplot() +
 aes(region = region, fill = id) +
 stamp_dk_brain(aes(fill = NULL, region = NULL)) +
 geom_dk_brain(alpha = .5)

dk_flat %>% 
  slice_sample(n = 5) %>% 
  mutate(id = sample(c(F,T),size = 5, replace = T)) %>% 
 ggplot() +
 aes(region = region, fill = id) +
 stamp_dk_brain(aes(fill = NULL, region = NULL)) +
 geom_dk_brain(alpha = .5)
```
